Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
adding conclusion

My heuristic evaluation for Google Maps focuses on the app's decision to not use standard iOS icons. One must recognize that using non-standard icons or processes isn't without drawbacks. It's loud. It's authorial voice. It's greater cognitive load for users. Anything inconsistent, first or third party is. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.

>>>>

My heuristic evaluation for Google Maps focuses on the app's decision to not use standard iOS icons. One must recognize that using non-standard icons or processes is not without drawbacks. Anything inconsistent, first or third party, is a greater cognitive load for users. On an integrated platform like iOS, integrating with the platform offers a lot of benefits, especially when it comes to user experience.
My heuristic evaluation for Apple Maps focuses on the placement of important functionality.
My judgment call on which device or system I feel performed best is Google Maps.
